### 2016-03-31 Draft.tex
Edits to simulation methods, including changing verbs to past tense.

We conduct three simulation studies to assess: (Sim 1) the importance of modeling detection heterogeneity via a partial finite-mixture component, (Sim 2) the impact of misspecifying the TTDD family (e.g., fitting an exponential TTDD model to data generated from a Weibull TTDD), and (Sim 3) model performance in a more complete scenario when both data generation and model fitting include covariates and random effects for abundance and detection.  
Because model behavior may differ between datasets with peaked and non-peaked TTDDs, we simulate both kinds of dataset for gamma, Weibull, and lognormal models.  
For all families, we simulate both mixture and non-mixture datasets.  
In total, we simulate 14 different dataset types.  
Counts are censored into nine-intervals as with the Ovenbird dataset.

In the first simulation study (Sim 1), for all 14 dataset types, we fit models with both mixture and non-mixture TTDD where the family is correctly specified.  
In Sim 2, we consider only mixture TTDD datasets, and we fit them with mixture TTDD models from all four families.  
For both Sim 1 and Sim 2, we simulate and model 16 replicates.  
In Sim 3, we repeat both the first two studies, but: (i) we include covariates and random effects described in Section \ref{sec:ovenbirdanalysis}, and (ii) we perform only a single replicate, because each gamma model takes an average of 5 days to fit.

For the first two simulation studies, we choose true parameter values so that: (i) the expected detection probability is 0.80, (ii) the expected count is the same as observed in the Ovenbird dataset, (iii) when there is a mixture component, we set $\gamma = 0.65$, meaning that 35\% of individuals are immediately detected, (iv) in non-peaked models, 70\% of \textit{detected} individuals are observed during the first two minutes, and (v) in peaked models, the detection mode for `hard to detect' individuals occurs at 5 minutes.  
For Sim 3, we set true parameter values for each dataset equal to the median posterior values obtained when fitting the same TTDD model to the Ovenbird data.  
Since all models applied to the Ovenbird data resulted in non-peaked model fits, we simulated peaked dataset variants by: (i) starting with posterior median Ovenbird estimates, (ii) setting the mixing parameter to $\gamma = 0.65$, and (iii) scaling the Intercept$^D$ and $\sigma_D^2$ terms by 0.25 and 1.1, which on average results in peak detection near 5 minutes and 75-85\% detection across all sites.  
Covariates and random effect levels are taken directly from the Ovenbird dataset.  
Unlike Sims 1 \& 2, overall detection probabilities in Sim 3 are not the same for each dataset.

>>>>

We conducted three simulation studies to assess: [Sim 1] the performance of modeling detection heterogeneity via a partial finite-mixture TTDD relative to a non-mixture TTDD, [Sim 2] the impact of misspecifying the TTDD family (e.g., fitting an exponential TTDD model to data generated from a Weibull TTDD), and [Sim 3] model performance in a more complete scenario when both data generation and model fitting include covariates and random effects for abundance and detection.  
Our simulations and models were from exponential, gamma, lognormal, and Weibull TTDD families.  
Because model behavior may differ between peaked and non-peaked datasets, we simulated both for all TTDD families except exponential.  
Thus, combined with partial finite-mixtures and non-mixtures, we simulated datasets from 14 different TTDDs in total.  
Counts were censored into nine-intervals as with the Ovenbird dataset.

In the first simulation study (Sim 1), for all 14 dataset types, we fit models with both mixture and non-mixture TTDD where the family was correctly specified.  
In Sim 2, we considered only mixture TTDD datasets, and we fit them with mixture TTDD models from all four families.  
For both Sim 1 and Sim 2, we simulated and modeled 16 replicates.  
In Sim 3, we repeated both the first two studies, but: (i) we included covariates and random effects described in Section \ref{sec:ovenbirdanalysis}, and (ii) we performed only a single replicate, because gamma models took an average of 5 days to fit.

Estimates from the Ovenbird analysis were used to inform simulation parameters except as follows.  
For Sim1 and Sim2, for consistency across simulations, we chose true parameter values so that: (i) the expected detection probability was 0.80, (ii) for mixture datasets, $\gamma = 0.65$ (meaning 35\% of individuals were immediately detected), (iii) in non-peaked models, 70\% of \textit{detected} individuals were observed during the first two minutes, and (iv) in peaked models, the detection mode for `hard to detect' individuals occured at 5 minutes.  
Since all models applied to the Ovenbird data resulted in non-peaked model fits, for Sim3 we simulated peaked dataset variants by:  (i) setting $\gamma = 0.65$, and (ii) scaling the Intercept$^D$ and $\sigma_D^2$ terms by 0.25 and 1.1, which resulted on average in peak detection near 5 minutes and 75-85\% detection across all sites.  
Unlike Sim1 and Sim2, overall detection probabilities in Sim 3 were not the same for each dataset.
